---
title: "Assignment1"
subtitle: "STATS 220 Semester 2022"
author: "Minghui Li "
date: "2022/3/19"
output: html_document
---
```{r}
library(magick)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo =TRUE ,message = FALSE)
```

## GitHub repository information: https://github.com/JeffPangding/STATS-220-.git

The repository shows the four favorite anime. They are Onepeice,dargon ball, naruto and slam dunk. 

```{r}
counts <- 4 : 1 %>% as.character()

circle_image <- image_read("https://cdn.britannica.com/25/172925-050-DC7E2298/black-cat-back.jpg") %>%
  image_scale(500)

circle_image1 <- image_read("https://cdn.britannica.com/87/205187-050-BEE2B338/tapetum-lucidum-light-retina-night-vision-vertebrates.jpg") %>%
  image_scale(500)

circle_image2 <- image_read("https://static.boredpanda.com/blog/wp-content/uploads/2021/02/602e59b32ea9d_c89bn5dgc1661__700.jpg") %>%
  image_scale(500)

circle_image3 <- image_read("https://www.boredpanda.com/blog/wp-content/uploads/2021/09/funny-cats-pictures-306-614083d845d32__700.jpg") %>%
  image_scale(500)

frame1 <- circle_image %>%
  image_annotate(text = "Be alert: Are you friend or foe", size = 30,color = "#FFB3FF") %>%
  image_scale(500) %>%
  image_extent("500x500")

frame2 <- circle_image1 %>%
  image_annotate(text = "I am watching you !!!", size = 40,color = "#FFB3FF" ) %>%
  image_scale(500) %>%
  image_extent("500x500")

frame3 <- circle_image2 %>%
  image_annotate(text = "Can I have a fish ??!", size = 50,color = "#FFB3FF",gravity = "center") %>%
  image_scale(500) %>%
  image_extent("500x500")

frame4 <- circle_image3 %>%
  image_annotate(text = "HOLLE, you want a ki...?" ,size = 30,color = "#FFB3FF") %>%
  image_scale(500) %>%
  image_extent("500x500")


frames <- c(frame1, frame2, frame3, frame4)

# creating an animation
image_animate(frames, fps = 0.5)
```

#Learning reflection
```{css}
h1 {color: white}
h3 {color: white}
h4 {color: white}


body {background-color: lightblue;}
  
p {font-family: verdana;font-size: 20px;color: white;}
```
   <p> One important thing that I learn from Module 1 creating HTML is GitHub learning. It lets me and others work together on projects from anywhere. This tutorial teaches you GitHub essentials like repositories, branches, commits, pull requests and use RMD file. GitHub Developer Peter Cottle created a fantastic activity that helps more visual learners learn about branching with Git. I can learn a lot of code in Github that I do not see before. For example, Learn to open my first pull request, make my first open source contribution, create a GitHub Pages site, and more.</p>
